---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gibberlite

```{r, echo = FALSE, results='asis'}
cat(
	badger::badge_devel("Glender/gibberlite", "purple"),
	badger::badge_github_actions("rossellhayes/ipa"),
	badger::badge_codecov("rcannood/princurve"),
	badger::badge_code_size("Glender/gibberlite")
)
```

## :arrow_double_down: Installation

You can install the development version of gibberlite from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Glender/gibberlite")
```
## Overview

With the gibberlite package you can sssess whether a sentence contains gibberish words. A Markov chain
inspects the sequence of vowels and consonents to estimate whether a sentence consists of natural words. Therefore,
words like 'asdfg' and 'dfrgfh' are considered unnatural and are classified as gibberish. The accuracy of the classification
improves when a sentence contains more characters. 

## :book: Usage

```{r}
library(gibberlite)
# create vector with character data
text <- c(
 "Personally I'm always ready to learn, although I do not always like being taught.",
 "asdfg",
 "Computer",
 "dfhdfghd",
 "I love to walk."
)

# assess if text is gibber
is_gibberish(text)
```

## :speech_balloon:

The gibberlite packages implements a very simple model. 
If you want a state-of-the-art solution, see the gibber package: https://github.com/Glender/gibber






